\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-10-15 demystify.tex

% \subsubsection{Strong Faculty vs High-ranked School}
% \begin{commentbox}[Thanh:]
% When considering PhD programs, we often wonder if we should prioritize a high-ranking university or a professor with a strong reputation? Of course, both are great, but it is hard to achieve both.  I believe receiving some guidance from you  would be incredibly valuable.
% \end{commentbox}

@@

If you want to contact a prof. to ask about \emph{research opportunities}, or \emph{funding} support, then \emph{yes}, I believe you should---it is \emph{worth it}. However, you need to do it the \emph{right way}.

>>>>

\begin{commentbox}[Xiaokuan]
Whether the student's research interest matches that of the advisor is very important;
if there is a mismatch,
either the student or the advisor has to make compromises,
which often leads to disagreements or conflicts. 
IMO, the advisor should be the one who {\it guides}  students to do research while allowing students to pursue their own interest,
instead of {\it dictating} their research.

\end{commentbox}
% \subsubsection{Strong Faculty vs High-ranked School}
% \begin{commentbox}[Thanh:]
% When considering PhD programs, we often wonder if we should prioritize a high-ranking university or a professor with a strong reputation? Of course, both are great, but it is hard to achieve both.  I believe receiving some guidance from you  would be incredibly valuable.
% \end{commentbox}

@@

If you want to contact a prof. to ask about \emph{research opportunities}, or \emph{GTA/GRA} support, then \emph{yes}, I believe you should---it is \emph{worth it}. However, you need to do it the \emph{right way}.

\xz{Applying for Ph.D. and contacting a potential Ph.D. advisor is a classic {\bf `why me, why you'} problem, 
similar to looking for a job in a company.
On a high level,
you need to show that you have done your {\it homework}
regarding the professor and the university,
and clearly explain:
1) why do you think you are a good fit in professor A's group?
2) why do you want to be advised by professor A, not B? 
3) why do you want to apply for university X, not Y?
If you don't want to spend time to do your homework,
the chance of getting a reply is close to zero.
}
